\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-05-05 paper_final.tex
Final Content check

We present an algorithm that teaches the desired concept to the Perceptron
learner when we know neither the learning rate, nor the initial weight vector of
our perceptron learner. The algorithm works well in general, but there is a very
unlikely case that will cause the number of unsupervised queries to diverge to
infinity. We also discuss a potential problem in the definition of the teaching
dimension and prove an upper bound on the teaching dimension in this setting
given an optimal algorithm for bounding $\eta$.

\subsection{$\epsilon$-Bounding the angle of $w_0$}
Our algorithm will only consider the decision boundary and the weight vector of
the Perceptron in two dimensions. In other words, we are considering the plane

defined by,
\[
  \begin{bmatrix}
    a & b & 0 & \cdots & 0
  \end{bmatrix} ^ \top
  \textnormal{where}
  \ a, b \in \mathbb{R}
\]
The decision boundary of the Perceptron passes through the origin, so it will
also pass through the origin of this plane and create a linear decision
boundary.
\\

@@

\section{Discussion}
Here we've shown some interesting bounds. Though not all tight they still highlight some of the security risks of perceptrons. If a perceptron were used on a web-server, any of these algorithms would be efficient enough to hack the perceptron to believe whatever decision boundary we like. As well these findings highlight the power of lying in Machine Teaching. With the ability to lie, teaching a perceptron becomes trivial. One further venture would be to look into other learning algorithms that could be taught efficiently with lying.

>>>>

We present an algorithm that teaches the desired concept to the Perceptron
learner when we know neither the learning rate, nor the initial weight vector of
our perceptron learner. The algorithm works well in general, but there is a very
unlikely case that will cause the number of unsupervised queries to diverge to
infinity. We also discuss a potential alteration to the definition of the teaching
dimension and prove an upper bound on the teaching dimension in this setting
given an optimal algorithm for bounding $\eta$.

\subsection{$\epsilon$-Bounding the angle of $w_0$}
Our algorithm will only consider the decision boundary and the weight vector of
the Perceptron in two dimensions. In other words, we are considering the plane defined by,
\[
  \begin{bmatrix}
    a & b & 0 & \cdots & 0
  \end{bmatrix} ^ \top
  \textnormal{where}
  \ a, b \in \mathbb{R}
\]
The decision boundary of the Perceptron passes through the origin, so it will
also pass through the origin of this plane and create a linear decision
boundary.

@@

\section{Discussion}
Here we've shown some interesting bounds. Though they are not all tight, they
still highlight some of the security risks of perceptrons. If a perceptron were
used on a web-server, any of these algorithms would be efficient enough to hack
the perceptron to believe whatever decision boundary we like. These findings
also highlight the power of lying in Machine Teaching. With the ability to lie,
teaching a perceptron becomes trivial. One extension would be to look into other learning algorithms that could be taught efficiently with lying.
